Computing exact restricted isometry constants via\\ mixed integer semidefinite programming

### 2015-02-09 RIP-MISDP-Paper/Paper_v1.tex
added a paragraph about SPCA to the introduction
added two papers about SPCA to the bib-file, the rest of the changes come from the 
formating of JabRef

One important condition is the \emph{restricted isometry property} (RIP),
which was first introduced by Cand\`es and Tao~\cite{CT05}. For each $k \in
\{1, \dots, n\}$, the RIP involves a \emph{restricted isometry constant}
$\delta_k$ depending on~$k$ and~$A$. If $\delta_k$ is sufficiently small
and there exists $\tilde{x} \in \R^n$ with $A \tilde{x} = b$ and
$\Norm{\tilde{x}}{0} \leq k$, then problems~\eqref{l0min} and~\eqref{l1min}
are equivalent; see Section~\ref{sec:RIP} for more details. There are
several types of matrices~$A$ for which the RIP holds, for instance random
matrices, see, e.g., Baraniuk et al.~\cite{BDDW08}. Although the RIP does
not provide necessary conditions, it is one of the major tools for
establishing for $\ell_0$-$\ell_1$-equivalence.

@@

However, one drawback of the RIP is that computing the restricted isometry
constants for a given matrix~$A$ and~$k$ is NP-hard, see~\cite{PT14}. One
the other hand, d'Aspremont et al.~\cite{Asp07,Asp08} proposed several
semidefinite relaxations to compute upper bounds on the restricted isometry
constants. Note that small upper bounds suffice to guarantee
$\ell_0$-$\ell_1$-equivalence between~\eqref{l0min} and~\eqref{l1min}, but
there exist cases in which the bounds are too weak to give a guarantee.

>>>>

One important condition is the \emph{restricted isometry property} (RIP),
which was first introduced by Cand\`es and Tao~\cite{CT05}. For each $k \in
\{1, \dots, n\}$, the RIP involves a \emph{restricted isometry constant}
$\delta_k$ bounding the $k$-sparse eigenvalues of $A$. If $\delta_k$ is sufficiently small
and there exists $\tilde{x} \in \R^n$ with $A \tilde{x} = b$ and
$\Norm{\tilde{x}}{0} \leq k$, then problems~\eqref{l0min} and~\eqref{l1min}
are equivalent; see Section~\ref{sec:RIP} for more details. There are
several types of matrices~$A$ for which the RIP holds, for instance random
matrices, see, e.g., Baraniuk et al.~\cite{BDDW08}. Although the RIP does
not provide necessary conditions, it is one of the major tools for
establishing for $\ell_0$-$\ell_1$-equivalence.

@@

However, one drawback of the RIP is that computing the restricted isometry
constants for a given matrix~$A$ and~$k$ is NP-hard, see~\cite{PT14}. On
the other hand, d'Aspremont et al.~\cite{Asp07,Asp08} proposed several
semidefinite relaxations to compute upper bounds on the restricted isometry
constants. Note that small upper bounds suffice to guarantee
$\ell_0$-$\ell_1$-equivalence between~\eqref{l0min} and~\eqref{l1min}, but
there exist cases in which the bounds are too weak to give a guarantee.

The relaxations in \cite{Asp07,Asp08} were originally derived for the deeply
connected problem of sparse principal component analysis (SPCA). Principal
component analysis (PCA) is about finding orthogonal directions maximizing the 
variance given in matrix $A$. SPCA tries to fix the problem that the components
of PCA usually consist of small contributions of all axes, which make the results
hard to interpret, by enforcing sparsity on the components. SPCA was
originally proposed by Zuo et al. in \cite{SPCA}, where a penalty term was added 
to the objective. Other authors like Moghaddam et al. in \cite{sbSPCA} also proposed 
computing a sparse maximal eigenvalue for SPCA, like it is done for the RIP.
